sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-26 doc/paper.Rmd
Fig tweaks

```{r}
g_pred <- ggplot(bc_coast_proj) +
  geom_sf(fill = NA, colour = "gray30", lwd = 0.3) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = exp(est))) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(
    limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x / 1000)
  ) +
  scale_y_continuous(
    limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x / 1000)
  ) +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  # scale_fill_viridis_c(trans = "sqrt", option = "B", begin = 0.3) +
  labs(fill = "Predicted\ndensity (units)", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"),
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, "pt")
  )
```

```{r, echo=FALSE}
blues <- RColorBrewer::brewer.pal(5, "Blues")
reds <- RColorBrewer::brewer.pal(5, "Reds")
g_mesh <- ggplot(pcod, aes(X, Y)) +
  inlabru::gg(mesh$mesh, edge.color = "grey60") +
  geom_point(alpha = 0.6, mapping = aes(size = density), colour = blues[4]) +
  theme_minimal() + coord_fixed() +
  labs(x = "UTMs E (km)", y = "UTMs N (km)") +
  scale_size_area(max_size = 10) +
  theme(legend.position = "none")
```

```{r}
nd <- data.frame(
  depth =
    seq(min(pcod$depth), max(pcod$depth), length.out = 300)
)
p_smooth <- predict(fit, newdata = nd, se_fit = TRUE, re_form = NA)
g_smooth <- ggplot(
  p_smooth,
  aes(depth, exp(est),
    ymin = exp(est - 1.96 * est_se),
    ymax = exp(est + 1.96 * est_se)
  )
) +
  geom_ribbon(fill = blues[2]) +
  geom_line(colour = blues[5], lwd = 1) +
  labs(x = "Depth (m)", y = "Density (units)") +
  xlim(min(pcod$depth), 300) +
  coord_fixed(expand = FALSE, ratio = 1.28)
```

@@

```{r pcod-fig, fig.cap="(ref:pcod-fig-cap)", fig.width=9, out.width="5.2in", fig.asp=1, fig.align='center'}
g_omega <- ggplot(bc_coast_proj) +
  geom_sf(fill = NA, colour = "gray30", lwd = 0.3) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = omega_s)) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(
    limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x / 1000)
  ) +
  scale_y_continuous(
    limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x / 1000)
  ) +
  # scale_fill_gradient2(high = reds[4], low = scales::muted("purple")) +
  scale_fill_gradient2(high = reds[4], low = blues[4]) +
  labs(fill = "Spatial random\nfield deviations", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"),
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, "pt")
  )
cowplot::plot_grid(g_mesh, g_smooth, g_omega, g_pred, labels = "auto")
```

@@

```{r owl-nao, fig.cap="(ref:owl-nao-fig)", out.width="3.5in", fig.align='center'}
owl <- here::here("figs", "owl_nao_effect.pdf")
if (!file.exists(owl)) {
  download.file("https://www.dropbox.com/s/fz1iw0a0diohyxc/owl_nao_effect.pdf?dl=1", 
    destfile = owl)
}
knitr::include_graphics(owl)
```

>>>>

```{r}
g_pred <- ggplot(bc_coast_proj) +
  geom_sf(fill = NA, colour = "gray30", lwd = 0.3) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = exp(est))) +
  coord_sf(datum = st_crs(utm_zone9)) +
  theme(panel.grid.major = element_line(colour = "grey90")) +
  scale_x_continuous(
    limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x / 1000)
  ) +
  scale_y_continuous(
    limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x / 1000)
  ) +
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  # scale_fill_viridis_c(trans = "sqrt", option = "B", begin = 0.3) +
  labs(fill = "Predicted\ndensity (units)", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"),
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, "pt")
  )
```

```{r, echo=FALSE}
blues <- RColorBrewer::brewer.pal(5, "Blues")
reds <- RColorBrewer::brewer.pal(5, "Reds")
g_mesh <- ggplot(pcod, aes(X, Y)) +
  inlabru::gg(mesh$mesh, edge.color = "grey60") +
  geom_point(alpha = 0.6, mapping = aes(size = density), colour = blues[4]) +
  coord_fixed() +
  labs(x = "UTMs E (km)", y = "UTMs N (km)") +
  scale_size_area(max_size = 10) +
  theme(panel.grid.major = element_line(colour = "grey90")) +
  theme(legend.position = "none")
```

```{r}
nd <- data.frame(
  depth =
    seq(min(pcod$depth), max(pcod$depth), length.out = 300)
)
p_smooth <- predict(fit, newdata = nd, se_fit = TRUE, re_form = NA)
g_smooth <- ggplot(
  p_smooth,
  aes(depth, exp(est),
    ymin = exp(est - 1.96 * est_se),
    ymax = exp(est + 1.96 * est_se)
  )
) +
  geom_ribbon(fill = blues[2]) +
  geom_line(colour = blues[5], lwd = 1) +
  labs(x = "Depth (m)", y = "Density (units)") +
  xlim(min(pcod$depth), 300) +
  coord_fixed(expand = FALSE, ratio = 1.28) +
  theme(panel.grid.major = element_line(colour = "grey90"))
```

@@

```{r pcod-fig, fig.cap="(ref:pcod-fig-cap)", fig.width=9, out.width="5.2in", fig.asp=1, fig.align='center'}
g_omega <- ggplot(bc_coast_proj) +
  geom_sf(fill = NA, colour = "gray30", lwd = 0.3) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = omega_s)) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(
    limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x / 1000)
  ) +
  scale_y_continuous(
    limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x / 1000)
  ) +
  # scale_fill_gradient2(high = reds[4], low = scales::muted("purple")) +
  scale_fill_gradient2(high = reds[4], low = blues[4]) +
  labs(fill = "Spatial random\nfield deviations", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"),
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, "pt")
  ) +
  theme(panel.grid.major = element_line(colour = "grey90"))
cowplot::plot_grid(g_mesh, g_smooth, g_omega, g_pred, labels = "auto", align = "hv")
```

@@

```{r owl-nao, fig.cap="(ref:owl-nao-fig)", out.width="3.9in", fig.align='center'}
owl <- here::here("figs", "owl_nao_effect.pdf")
if (!file.exists(owl)) {
  download.file("https://www.dropbox.com/s/fz1iw0a0diohyxc/owl_nao_effect.pdf?dl=1", 
    destfile = owl)
}
knitr::include_graphics(owl)
```
